%Compiled with LuaLaTeX with fontspec
\documentclass[]{friggeri-cv}
\hypersetup{%
  colorlinks=true,% hyperlinks will be black
  linkcolor=green,% hyperlink borders will be red
  pdfborderstyle={/S/U/W 1}% border style will be underline of width 1pt
}
\definecolor{mygrey}{gray}{0.4}
\newcommand{\email}{\underline{\href{mailto:g@gleech.org}{Email}}}%
\newcommand{\predictions}{\underline{\href{http://predictionbook.com/users/technicalities}{Predictions}}}%
\newcommand{\linkedIn}{\underline{\href{https://linkedin.com/in/gleech}{LinkedIn}}}%
\newcommand{\github}{\underline{\href{https://github.com/g-leech}{Github}}}%
\newcommand{\newBlog}{\underline{\href{www.gleech.org}{Blog}}}%
\newcommand{\aidImpact}{\underline{\href{https://www.gleech.org/aid}{Aid impact bounds}}}%
\newcommand{\hmms}{\underline{\href{https://www.gleech.org/accommodation}{Speaker similarity}}}%
\newcommand{\analogies}{\underline{\href{https://www.gleech.org/conversion/}{Formal analogies}}}%
\newcommand{\nonvicious}{\underline{\href{https://www.gleech.org/automatic}{Automation \& welfare}}}%
\newcommand{\latex}{\underline{\href{https://www.gleech.org/cv.tex}{LaTeX}}}%
%
\newcommand{\livingWage}{\underline{\href{https://www.gleech.org/maximum}{Maximum wage}}}% 
\newcommand{\dataScience}{\underline{\href{http://gleech.org/data-science}{On data science}}}%
\newcommand{\axaJob}{\href{https://web.archive.org/web/20170113182017/https://www.kaggle.com/jobs/17128/axa-insurance-data-scientist-london}{\textbf{Data Scientist}}}% 
\newcommand{\controversy}{\underline{\href{http://gleech.org/controversy}{Controversy vs impact}}}%
\newcommand{\odyssey}{\underline{\href{https://docs.google.com/spreadsheets/d/1eAe55oEzFhSFB5qNZYMzjSRLcJOW34_DxdAscXSu0AQ/edit?usp=sharing}{vs publication bias}}}%
\newcommand{\json}{\underline{\href{https://github.com/gavin-leech/MachineCV/blob/master/jobs_4_machines.json}{Career JSON}}}%
\newcommand{\furoJob}{\href{https://web.archive.org/web/20170113184959/https://1.bp.blogspot.com/-8MTHkoAbScc/WHkd2EI0liI/AAAAAAAAC1k/0ZWr2XpO_ewW3Hd1RDHTfv3O_jki3bNigCLcB/s1600/furo.png}{\textbf{\textbf{Frontend Developer}}}}%
\newcommand{\freeJob}{\href{http://web.archive.org/web/20170113190649/http://www.freetobook.com/}{\textbf{Software Developer}}}%
\newcommand{\stugoJob}{\href{http://web.archive.org/web/20170113185418/http://stugo.co.uk/}{\textbf{Graduate Software Developer}}}%
\newcommand{\govJob}{\href{http://web.archive.org/web/20170113190449/http://www.gov.scot/Resource/0047/00478784.pdf}{\textbf{Assistant Statistician}}}%
\newcommand{\standJob}{\href{http://web.archive.org/web/20170113190135/http://standinternational.org/about-us}{\textbf{\,\,Database Developer}}}%
\newcommand{\altHmms}{\underline{\href{https://www.gleech.org/accommodation}{Hidden Markov Models in the study of accommodation}}}%
\newcommand{\altAid}{\underline{\href{https://www.gleech.org/aid}{Evaluating aid abolitionism}}}%
\newcommand{\sparkCert}{\underline{\href{http://www.oreilly.com/data/sparkcert.html}{O'Reilly Developer Certification for Spark}}}%
\newcommand{\scala}{\underline{\href{https://www.coursera.org/specializations/scala}{Odersky`s Scala Specialisation}}}%
\newcommand{\iq}{\underline{\href{https://2.bp.blogspot.com/-T72346JIUhk/WKnGhDfOZTI/AAAAAAAAC2Q/08OJLVovi64flXyfz0RsSZ6mNsjSlvUCACLcB/s1600/2017-02-10-153628.jpg}{IQ: 99th percentile}}}
\begin{document}
%
\header{gavin\,}{leech}
       {data scientist, software developer} %/ research parasite}
%
\begin{aside}
  \section{about}
    London based.
    ~
    \email{}
    \github{}
    \newBlog{}
    \linkedIn{}
  	~
  	~
  \section{research} 
	\hmms{}
  	\aidImpact{}
  	\nonvicious{}
    \dataScience{} 
  	\livingWage{}
    \controversy{}
   	\analogies{}
%
  ~
  ~
  \section{programming}
    Python/SciPy/Spark, Keras, *nix, C\#, JS (ES6, node), PHP, Scala, Pig, \latex{} ...Powershell.
  ~
  ~
  \section{metadata}
    %\iq{}
    \odyssey{}
	\json{}
  	%\antiresume{}
  	%\pwem{}
\end{aside}

\smallskip
\section{interests}

effective altruism, failures of human reasoning, failures of human reasoning about human reasoning, statistics as applied philosophy, data mining as conceptual analysis, lists.\\
%
\\
\section{experience}
\begin{entrylist}
	\smallskip\smallskip
	\entry
	{Sep‘16 – Now}
	{\axaJob{}}
    {AXA Insurance, London}
    {Creating machine learning models (GLMs, GBMs, ANNs) for pricing, medical risk, image recognition on architectural plans; scraping at scale; orchestrating a TB/day Hadoop pipeline. I head a team of 3 junior engineers \& scientists.\\
     \textit{Buzzwords:}	Python, Spark, Keras, Jupyter, Hadoop, Oozie, Avro, Pig, Pytest. }		
    
    \smallskip\smallskip    \smallskip\smallskip \smallskip\smallskip
	\entry
	{May – Aug‘16}
	{\furoJob{}}
    {Furo, London}
    {Helped on a fresh procurement web app. Sole responsibility for design \& implementation of a tendering system, through TS controllers from APIs. \\
    \textit{Buzzwords:}	C\# 6, Typescript, Angular, Visual Studio/SQL Server, Bitbucket. }	
    \smallskip\smallskip\smallskip\smallskip \smallskip\smallskip
    
    \entry
	{Oct‘15 – Jun‘16}
	{\freeJob{}}
    {Freetobook, Glasgow}
    { Worked on a large legacy accommodation engine: PHP back-end, JS front-end, REST APIs.
    Sole design of secure, PCI compliant, credit-card storage. \\
	\textit{Buzzwords:}	PHP (5 \& 7), LAMP, SQL, Laravel, cURL, Gitlab, New Relic. }	
	\smallskip\smallskip	\smallskip\smallskip	\smallskip\smallskip
	
	\entry
	{Jun – Sep‘15}
	{\stugoJob{}}
    {Stugo, Glasgow}
    { Jumped into web tech from scratch; wrote first production code within 2 weeks, deployed to pharmacies worldwide. Worked on a medicine pump manager (C\#) \& a secure pharmacy record system (nodeJS). 4th employee. 
    \\
	\textit{Buzzwords:}	C\#, WPF, node.JS, MEAN, Ractive, Mongo, Vagrant, VMWare. }	
	\smallskip\smallskip	\smallskip\smallskip	\smallskip\smallskip
	
	\entry
	{Dec‘14 – May‘15}
	{\standJob{}}
    {STAND International, Edinburgh}
    {\,\,Built a small ops database for an international NGO. Greenfield design \& deployment; using the 365 nonprofit licence, I delivered this at zero cost. \\
	\,\,\textit{Buzzwords:}	MS Access, Office365, SQL, UML, data protection. }
	\smallskip\smallskip	\smallskip\smallskip	\smallskip\smallskip
	
	\entry
	{Jan – Apr‘14}
	{\govJob{}}
    {The Scottish Government, Edinburgh}
    {Produced \& explained official stats for Education Analytical Services. Worked on the `Insight' reporting platform, giving teachers hard data \& viz on their classes \& themselves. Prepped the national Social Care Survey 2015. \\
	\textit{Buzzwords:}	SAS, SQL, OLAP, PCA, data protection, official statistics. }\\
\end{entrylist}
% 
\\\\
\section{software}
% 
\begin{entrylist}
  \entry
    {2017}
    {sesame: SEarch for StAtistical MEthods}
    {\href{}{work in progress}}
    {Decision trees / search engine for which stats you can/should use. Scala.js}
\\
  \entry
    {2017}
    {The First Computers}
    {\href{https://www.gleech.org/first-computers/}{deployed here}}
    {Tiny app (and a conceptual analysis) to solve a historical question. Uses the Transcrypt Python transpiler - unfortunately.}
\\
  \entry
     {2016}
     {modernlove}
     {\href{}{work in progress}}
     {A visualiser for sexualities. Python / Django / nose / seaborn }
\\
  \entry
    {2015}
    {Py2HTK}
    {\href{https://github.com/g-leech/Py2HTK}{github here}}
    {Wrapper for venerable (creaky) ML library, the Hidden Markov model ToolKit. }

\end{entrylist}
\\\\
\section{education}
\begin{entrylist}
  \entry
    {2013 – Now}
    {BSc Mathematics \& Statistics}
    {The Open University}
    {Proper foundation: Analysis, probability theory, functional analysis, linear algebra, ODEs \& PDEs, experiment design and RCTs, sampling theory, classical mechanics \& field theory, stochastic processes, medical statistics, Bayesian modelling, thus far. Part-time during full-time work.}\smallskip \\
    
  \entry
    {2014 – 2015}
    {MSc Software Development}
    {University of Glasgow}
    {Conversion Masters: Java, SQL, HTML/CSS/PHP, MC6800 assembly plus 'patterns, data structures \& algorithmics. The psychology of security, law of safety-critical systems, design of UX. Thesis in computational linguistics: '\altHmms{}'.} \smallskip\\
  \entry
    {2008 – 2012}
    {MA (Hons) Economics with Philosophy} 
    {University of Aberdeen}
    {Topics covered included formal logic, micro- \& macro- economics, rudimentary
statistics, health policy, development policy. I received a four-year Alumni Fund scholarship on merit. Dissertation in foreign aid effectiveness: '\altAid{}'.}
%  \entry
%    {2017}
%    { Various online certificates }
%    {Databricks, Coursera, edX}
%    {\sparkCert{}; \scala{}; the Microsoft Professional Degree in Data Science (engineering \& analysis with T-SQL, PowerBI, R, Azure ML, HDInsight, Cortana).}\smallskip  
\end{entrylist}
\end{document}
